Navigating to a greener Europe with 24/7 hourly clean electricity procurement

### 2023-04-16 manuscript/sections/results.tex
finish results section

A prominent observation in \cref{fig:10-hourly-annual.pdf} is that 100\% annual matching (or any other volumetric-based matching policy) has a proportionally smaller effect on a system decarbonisation than 24/7 hourly matching in 2030 compared to 2025. 
This result is driven by the diminishing value of each additional megawatt of capacity of non-dispatchable generators, i.e., self-cannibalisation of solar and wind generators. 
The 24/7 hourly CFE matching have a stronger decarbonisation impact in a cleaner systems due to (i) the profile mechanism, (ii) the volume mechanism, since the procured resources have a more diverse portfolio including battery storage, long-duration energy storage or advanced clean firm technologies that allow for having clean electricity available in periods when system-wide wind and solar generation is scarce.

>>>>

A prominent observation in \cref{fig:10-hourly-annual.pdf} is that 100\% annual matching has a proportionally smaller effect on a system decarbonisation than 24/7 hourly matching in 2030 compared to 2025. 
This result is driven by the diminishing value of each additional megawatt of capacity of non-dispatchable generators, i.e., self-cannibalisation of solar and wind generators. 
The 24/7 hourly CFE matching have a stronger decarbonisation impact in a cleaner systems due to (i) the profile mechanism, (ii) the volume mechanism, since the procured resources have a more diverse portfolio including battery storage, long-duration energy storage or advanced clean firm technologies that allow for having clean electricity available in periods when system-wide wind and solar generation is scarce.

The decarbonisation mechanisms discussed above suggest a displacement of fossil-fueled generators in the rest of the system in presense of voluntary clean electricity procurement.
We illustrate this effect in \cref{fig:10-2030-DE-p1-system_capacity_diff.pdf}, which shows the difference in the generation capacity expansion of the whole European electricity system (excluding resources procured by participating customers) with and without commitments to clean electrity procurement (an illustraive scenario for Germany, 2030, technological palette~1). 
Hourly CFE procurement benefits the system by having a pronounced effect of flexibility needs reduction -- the system requires less battery storage and less peaker capacity in a form of \gls{ocgt}. 
In the selected example, 3.8~GW of load (10\% of \gls{ci} sectors in Germany) participate in the procurement.
In a case of hourly matching with 100\% CFE target, this reduces \gls{ocgt} investments by 4.6~GW and battery storage by 2.6~GW in the rest of the system.
The substitution of gas-fired capacity with clean resources procured by \gls{ci} consumers facilitates decarbonization of the entire system, as shown above.
